Cluster Difference Imaging Photometric Survey (CDIPS) II: A Validated Jupiter-Sized Planet in IC~2602

### 2020-06-18 paper/ms.tex
WIP manuscript

\title{
  Cluster Difference Imaging Photometric Survey (CDIPS) II:
  Validatation of a Jupiter-Sized Planet in IC~2602
}

@@

\begin{abstract}
  We report the discovery of TOI 837.01 and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA {\it Transiting Exoplanet Survey Satellite} (TESS), the ESA
  Gaia mission, ground-based photometry, and spectroscopy from
  CTIO1.5/CHIRON, MPG2.2/FEROS, and AAT/Veloce.  We find that
  TOI$\,$837 is a $T=9.9$ G-dwarf in IC~2602 (the ``Southern
  Pleiades'').  The star and validated planet are therefore 30$\pm$20
  million years old.  The planet is warm ($P = 8.YY\,{\rm d}$) and
  roughly Jupiter-sized.  However, its transits are grazing: $b >
  0.92$ at 3$\sigma$.  From TESS photometry alone, the planetary size
  lies within 0.58--3.87 $R_{\rm Jup}$, due to the degeneracy between
  the planetary size and the impact parameter of the transit.  From
  radial velocity monitoring, we limit the mass of planet to less than
  2.XX $M_{\rm Jup}$ (3$\sigma$).  Grazing transits are cause for
  concern, as they usually are indicative of astrophysical false
  positive scenarios.  Our follow-up data render such scenarios highly
  unlikely.  Multi-color photometry requires eclipsing companions to
  have nearly identical color as TOI$\,$837, eliminating hierarchical
  eclipsing binary scenarios.  Background eclipsing binary scenarios
  are limited by speckle imaging, but formally remain a 0.2\%
  possibility.  TOI 837.01 is therefore a validated adolescent exoplanet
  orbiting a bright host star.
  Further analysis of its mass, atmosphere, and obliquity should
  confirm its planetary nature beyond doubt, and are worthwhile
  because young planets are expected to do interesting things.
\end{abstract}

%FIXME these keywords.
\keywords{
	Exoplanets (XXX),
	Exoplanet evolution (491),
	Stellar ages (1581),
	Young star clusters (XXX)
}

@@

Recently, young planets have been hype.

%TODO: pull from the cdips repo! I already wrote a lot of this...

TESS \citep{ricker_transiting_2015}.

>>>>

\title{
  Cluster Difference Imaging Photometric Survey (CDIPS) II:
  A Validated Jupiter-Sized Planet in IC~2602
}

@@

% TODO: SpType subtype?
\begin{abstract}
  We report the discovery of TOI 837.01 and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA {\it Transiting Exoplanet Survey Satellite} (TESS), the ESA
  Gaia mission, ground-based photometry, and spectroscopy from
  CTIO1.5/CHIRON, MPG2.2/FEROS, and AAT/Veloce.  We find that
  TOI$\,$837 is a $T=9.9$ G-dwarf in IC~2602 (the ``Southern
  Pleiades'').  The star and validated planet are therefore 30$\pm$20
  million years old.  The planet is warm ($P = 8.YY\,{\rm d}$) and
  roughly Jupiter-sized.  However, its transits are grazing: $b >
  0.92$ at 3$\sigma$.  From TESS photometry alone, the planetary size
  lies within 0.58--3.87 $R_{\rm Jup}$, due to the degeneracy between
  the planetary size and the impact parameter of the transit.  From
  radial velocity monitoring, we limit the mass of planet to less than
  2.XX $M_{\rm Jup}$ (3$\sigma$).  Grazing transits are cause for
  concern: they usually are indicative of astrophysical false
  positive scenarios.  Our follow-up data render such scenarios highly
  unlikely.  Multi-color photometry requires eclipsing companions to
  have nearly identical color as TOI$\,$837, eliminating hierarchical
  eclipsing binary scenarios.  Background eclipsing binary scenarios
  are limited by speckle imaging, but formally remain a 0.2\%
  possibility.  TOI 837.01 is therefore a validated adolescent
  exoplanet.  Further analysis of its mass, atmosphere, and obliquity
  should confirm its planetary nature beyond doubt, and will improve
  our understanding of how the physical and orbital properties of
  exoplanets change in time.
\end{abstract}

\keywords{
	Exoplanets (498),
  Transits (1711),
	Exoplanet evolution (491),
	Stellar ages (1581),
	Young star clusters (1833)
}

@@

Over the first hundred million years of their lives, exoplanetary
systems are expected to undergo major physical and dynamical changes.
For a typical Sun-like star, the protoplanetary disk is observed to
dissipate within $\sim$3 million years (CITE).  The planet formation
process presumably finishes within this time for gas giants (CITE).
The rocky planet population will also be mostly evolved within $\sim$3
million years (CITE), but it may undergo significant changes over the
next $\sim$10-100 million years through giant impacts.  In the solar
system, for instance, the Moon was thought to be formed at an age of
XX million years through such an impact (CITE).

A number of other processes are thought to happen relatively quickly.
Physical changes in the sizes of planets are expected as they
contract, and as their atmospheres undergo photoevaporation (CITE,
CITE).  The relative importance of these two processes is set by the
planetary mass, as well as the radiation environment.
Photoevaporation in particular can be directly observed in {\it e.g.},
the He 10830\AA\ line (CITE, CITE).  Dynamical changes are expected in
the semi-major axes, eccentricities, and stellar obliquities of young
planets.  When the gas disk is present, the planetary semi-major axis
is thought to change due to viscous coupling (CITE).
High-eccentricity migration processes including planet-planet
scattering (CITE), secular chaos (CITE), and Kozai-Lidov oscillations
(CITE) can also occur.  The circularization timescale is thought to be
such that for any giant planets that migrated early, their orbits
should circularize within 100 million years (CITE).

The topic of exoplanetary evolution through time has enticed many
observers.  However, since most dwarf stars do not appreciably change
until evolving off the main sequence, creative approaches must be used
to infer stellar ages \citep{soderblom_ages_2010}.  One approach
beginning to bear fruit in exoplanet studies is to search for planets
in coeval groups of stars, hereafter ``clusters''.  This includes the
open clusters of yore, as well as the moving groups and stellar
associations that began to be uncovered in the late 1990s
\citep{zuckerman_young_2004}.  The ages of these stellar ensembles are
inferred through isochrone analyses of color-magnitude diagrams, using
a combination of main-sequence turnoff locations,
pre-main-sequence isochronal tracks, and averaged MS isochronal ages
across known cluster members \citep[{\it e.g.},][Section
3.4.3]{kharchenko_global_2012}.  Once calibrated, gyrochronology can
also be used to verify the age of a stellar ensemble (CITE: Angus too) \citep[{\it
e.g.},][]{barnes_color-period_2015,meibom_spin-down_2015,curtis_tess_2019}.
The ages of planets discovered in these cluster stars are then assumed
to equal the age of the larger stellar ensemble.

The first planets to be detected in open clusters were found through
radial velocity (RV) measurements of red giants in the Hyades and
NGC~2423 \citep{Sato_et_al_2007,lovis_mayor_2007}.  Subsequent
spectroscopic searches in Praesepe led to the detection of the first
hot Jupiter in a cluster \citep{Quinn_et_al_2012}, and also the first
multi-planet system in a cluster \citep{Malavolta_et_al_2016}.
Surveys of pre-main sequence T Tauri stars in the Taurus star-forming
region have also led to the youngest hot Jupiters yet reported
\citep[V830~Tau~b and
CI~Tau~b][]{donati_hj_2016,johns-krull_candidate_2016,flagg_co_2019}.
A final RV survey of note was conducted by
\citet{brucalassi_search_2017}, who followed 88 stars in M~67 over 7
years.  They reported detections of three hot Jupiters around main
sequence stars, and of one giant planet around an evolved star.

The transit method was comparatively slow to catch up.  Deep transit
searches typically comprising days to weeks of observations were
performed for NGC~2158, 6791, and 1245, among other clusters
\citep{mochejska_planets_2005,mochejska_planets_2006,burke_survey_2006}.
Related projects include a search of M~37 by
\citet{hartman_MMT_IV_2009}, of Praesepe by
\citet{pepper_photometric_2008}, and of nine young clusters in the
solar neighborhood by the Monitor team
\citep{aigrain_monitor_2007,irwin_monitordata_2007,miller_monitor_2008}.
Though these studies led to measurements of stellar rotation periods
\citep{hartman_rotation_2009,Irwin_NGC2516_2007} as well as the
discovery of pre-main-sequence (PMS) eclipsing binaries (EBs)
\citep{irwin_monitor_PMSEB_2007}, no definitive transiting planets in
open clusters were found.  Transit searches in globular clusters were
similarly met with null results \citep{gilliland_lack_2000,
weldrake_searching_2006} (CITE: Masuda).  These searches were
typically sensitive to planets larger than Jupiter, on $\lesssim 3$
day orbital periods.  Hot Jupiter occurrence rate limits were derived
at the $\lesssim 5\%$ level \citep[{\it e.g.},][]{burke_survey_2006,
hartman_MMT_IV_2009}.  The modern 0.5-1\% occurrence rate suggests
that these early transit surveys needed a greater data volume, at
higher precision for detection to be possible
\citep{mayor_harps_2011,wright_frequency_2012,howard_planet_2012,petigura_metallicity_2018}.

Kepler \citep{borucki_kepler_2010} observed enough stars for long
enough and with sufficient precision to detect transiting planets in
open clusters:  Kepler-66b and 67b, in the gigayear-old NGC~6811
\citep{Meibom_et_al_2013}.  Though a broken reaction wheel ended the
prime Kepler mission, the repurposed K2 \citep{howell_k2_2014}
switched between fields along the ecliptic every quarter-year, and was
able to observe far more clusters and young stars.  The resulting
discoveries made by K2 through its surveys of the Pleiades, Hyades,
Praesepe, and Upper Sco were a major inspiration for the present work.

K2-25b, discovered in the Hyades, has a radius ($3.43\,R_\oplus$) that
is larger than older Kepler planets around M dwarfs at similar insolation levels
\citep{Mann_K2_25_2016}.  This inflated radius is perhaps a hint that
the planet is contracting, or losing its atmosphere \citep[{\it
e.g.},][]{Fortney_et_al_2007,Owen_Wu_2013,Fulton_et_al_2017}.  The
super-Neptune sized K2-33b ($P\approx 5.4\,{\rm d}$), found in Upper
Sco, showed that at least some close-in planets must form within about
10 Myr \citep{Mann_K2_33b_2016,David_et_al_2017}.  Further discoveries
included six transiting planets in Praesepe
\citep{obermeier_k2_2016,Mann_et_al_2017}, a long-period candidate
super-Earth in the Hyades \citep{vanderburg_zeitVII_2018}, the
three-planet K2-136 system in the Hyades
\citep{ciardi_k2-136_2018,livingston_three_2018,mann_ZEITVI_2018}, and
later the two-planet system K2-264 in Praesepe
\citep{rizzuto_zeitVIII_2018,livingston_k2-264_2019}.  There has also
recently been a detection by K2 of a Jupiter-sized planet orbiting
every 24 days around V1298~Tau \citep{david_v1298_2019}.

A significant amount of effort continues to be devoted towards the
discovery and characterization of planets around young stars.
Sometimes, cluster membership may not even be necessary, if a star's
youth can be inferred from combined rotation, activity, and kinematic
indicators \citep[{e.g.}, K2-233;][]{david_k2-233_2018}.  To
investigate demographics in time, the detection sensitivities and
reliabilities of these searchers need to be calibrated, likely with a
machinery similar to that outlined by \citet{rizzuto_zeitV_2017}.  A
separate requirement for population studies to be statistically
robust, imposed by the geometric rarity of transits, is that many tens
of thousands of stars with known ages must be monitored at high
precision.

The TESS mission \citep{ricker_transiting_2015}, though designed for
other purposes, holds the promise to deliver the most homogeneous and
comprehensive cluster photometric survey in history.  More
quantitatively, the \citet{Kharchenko_et_al_2013} cluster member
database indicates that $\approx 2\times10^5$ open cluster members
brighter than $T=16$ will be observed in the full-frame images over
the first two years of TESS observations.  This count includes the
``most probable'' members within each cluster's radius, which by the
\citet[][]{kharchenko_global_2012} definition requires the independent
kinematic, photometric, and spatial membership probabilities to each
exceed 61\%.  The actual number of stars in clusters may be larger, as
the membership catalogs are not yet complete, even at these relatively
bright magnitudes \citep[{\it
e.g.},][]{roser_nine_RSG_2016,cantat-gaudin_gaia_2018,cantat-gaudin_newOCs_2019}.
